Master's Project Journal

### 2019-04-06 conf_paper/paper.tex
ieeetran fixed
as
initial thesis background

\author{\IEEEauthorblockN{C. Dooley, E. Blokhina, B. Mulkeen}
    \IEEEauthorblockA{\textit{School of Electrical \& Electronic Engineering, University College Dublin}
    	\vspace{-1.2cm}

@@

\begin{table}[!ht]
    \begin{center}
        \begin{tiny}
        	\setlength{\tabcolsep}{.9\tabcolsep}
            \begin{tabular}{cc|c|c|c|c|c|c|}           
                \cline{3-8}
                && \multicolumn{3}{c|}{Jitter Standard Deviation (ns)} & \multicolumn{3}{c|}{Max. Time Interval Error. (ns)} \T\\
                \cline{3-8} 
                &&PLL 11&PLL 12&PLL 22&PLL 11&PLL 12&PLL 22\T\\
                \hline
                \multicolumn{2}{|l|}{Osc 1, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &1.4377 &1.4714&1.4217  &6.1910&6.3667&6.8052 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.91589&1.0993&1.0875  &8.3619&8.9768&10.974 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &1.0470 &1.0979&1.0306  &24.998&33.767&33.204 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &0.56728&0& 0&5.3797&0&0 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.57365&0& 0&6.0632&0&0 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &0.58760&0& 0&15.466&0&0 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET B}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &0.71635&0&0  &4.8293&0&0 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.76883&0&0  &4.7922&0&0 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &0.79292&0&0  &6.5277&0&0 \T\\
                \hline
                \B
                %% old 2b
                %&7.8090&7.8827&6.6272   &17.336&21.151&24.302
                %&7.7866&8.1145&7.3598   &17.649&29.962&37.051
                %&7.7575&7.7729&6.6962   &30.019&40.577&45.617
                %% old 2a
                %&78.458&74.025&67.779  &146.09&143.70&142.03
                %&78.428&72.646&65.665  &146.23&298.49&200.10
                %&78.436&73.827&67.648  &235.73&497.60&311.28

@@

            \end{tabular}
        \end{tiny}
        \caption{}
        \label{table:b_c_perf}
    \end{center}
\vspace{-0.5cm}
\end{table}
From the table it is apparent that the coarser period and detection steps of Design ``1A''  (3.875 nanoseconds as at greater clock frequencies timing violations would occur) cannot deliver the same jitter performance as the inverter ring driven designs. Looking at the two subsequent designs their lesser flexibility is made up for by their more realistic jitter behaviour. As would be expected best performance occurs when the network is in PLL mode and as the quality of the reference degrades as the network is connected up performance becomes worse. In terms of cycle-to-cycle jitter the best performing design is that of ``2A'', however, its time interval error is significantly worse especially in bilateral network mode. This more aggressive degradation as the network is linked up can be attributed to the worse detection resolution of the FPGA clocked phase detector, four times worse than the 1.2 second step of the entirely inverter based Design ``2B''.\\
The further a PLL is away from the reference feeding ADPLL 11 the worse performance is, peaking furthest from the reference in ADPLL 22.
%TODO insert comment here when I have more oscillators for 1 lines or so.

The lesser cycle-to-cycle of Design ``2A'' follows from the implementation independent design of the phase detector. Unlike the inverter based design where the implementation may result in the propagation delay between taps on the delay line changing, from both tap to tap in the same detector and the same tap in different detectors, the clocked design has identical detection resolutions as each register is driven by the FPGA clock. This can be highlighted in the more easily demonstrable case of the clocked and inverter based oscillators.\\
\begin{figure}[h]%
    \centering
    \subfloat[Inverter Based Design.]{{\includegraphics[width=0.5\linewidth]{distrib_ring} }}%
    \subfloat[FPGA Clocked Design.]{{\includegraphics[width=0.5\linewidth]{distrib_pa} }}%
    \caption{Example Distribution of Periods.\label{fig:dists}}    
    \vspace{-0.5cm}
\end{figure}
Figure \ref{fig:dists} paints a picture of the unrealistic nature of the FPGA clocked design in comparison to its inverter based counterpart, each oscillator will have identical intrinsic period steps thus eliminating any jitter that maybe be seen in the system due to misalignment. This effects the suitability of the FPGA clocked designs for the improvement of simulation models, or the examination of how a novel block may impact the behaviour of the network.
\section*{Conclusion}
An FPGA is a suitable environment for the prototyping of ADPLL networks and can fill a number of roles depending on the designer's requirements. However, the designer should bear in mind the platform's limitations, especially when attempting to use a frequency that is not orders of magnitude lower than the maximum clock available from the FPGA's clock manager. Inverter based and FPGA clocked designs, both have a niche in which they are the preferred option, with the clocked design better suiting replication of an existing design at scaled-down frequencies and the inverter based designs better in the modelling and analysis of ADPLL network behaviour.

\bibliographystyle{ieeetran}
\bibliography{conf}

>>>>

\author{\IEEEauthorblockN{C. Dooley$^1$, E. Blokhina$^1$, B. Mulkeen$^1$, D. Galayko$^2$}
    \IEEEauthorblockA{\textit{$^1$School of Electrical \& Electronic Engineering, University College Dublin}\\
    \textit{$^2$LIP6 Lab, Sorbonne Université}
    	\vspace{-0.8cm}

@@

\begin{table}[!ht]
    \begin{center}
        \begin{tiny}
        	\setlength{\tabcolsep}{.9\tabcolsep}
            \begin{tabular}{cc|c|c|c|c|c|c|}           
                \cline{3-8}
                && \multicolumn{3}{c|}{Jitter Standard Deviation (ns)} & \multicolumn{3}{c|}{Max. Time Interval Error. (ns)} \T\\
                \cline{3-8} 
                &&PLL 11&PLL 12&PLL 22&PLL 11&PLL 12&PLL 22\T\\
                \hline
                \multicolumn{2}{|l|}{Osc 1, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &1.4377 &1.4714&1.4217  &6.1910&6.3667&6.8052 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.91589&1.0993&1.0875  &8.3619&8.9768&10.974 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &1.0470 &1.0979&1.0306  &24.998&33.767&33.204 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &0.56222&0.49224&0.64124 &5.3039&7.8626&5.4634 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.55040&0.51284&0.62796 &5.5312&7.5359&7.9697 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &0.57056&0.50403&0.61644 &11.515&15.943&17.428 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET B}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &0.66757&0.84477&0.71308 &5.9142&6.1353&5.3939 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.66934&0.83894&0.71271 &5.8779&7.1746&6.8914 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &0.68372&0.83193&0.68570 &7.5705&9.6292&9.7715 \T\\
                \hline
                \B
                %% old 2b
                %&7.8090&7.8827&6.6272   &17.336&21.151&24.302
                %&7.7866&8.1145&7.3598   &17.649&29.962&37.051
                %&7.7575&7.7729&6.6962   &30.019&40.577&45.617
                %% old 2a
                %&78.458&74.025&67.779  &146.09&143.70&142.03
                %&78.428&72.646&65.665  &146.23&298.49&200.10
                %&78.436&73.827&67.648  &235.73&497.60&311.28

@@

            \end{tabular}
        \end{tiny}
        \caption{}
        \label{table:b_c_perf}
    \end{center}
\vspace{-0.5cm}
\end{table}
From the table it is apparent that the coarser period and detection steps of Design ``1A'' (3.875 nanoseconds as at greater clock frequencies timing violations would occur) cannot deliver the same jitter performance as the inverter ring driven designs. Looking at the two subsequent designs their lesser flexibility is made up for by their more realistic jitter behaviour. As would be expected best performance occurs when the network is in PLL mode and as the quality of the reference degrades as the network is connected up performance becomes worse. In terms of cycle-to-cycle jitter the best performing design is that of ``2A'', however, its time interval error is significantly worse especially in bilateral network mode. This more aggressive degradation as the network is linked up can be attributed to the worse detection resolution of the FPGA clocked phase detector, four times worse than the 1.2 nanosecond step of the entirely inverter based Design ``2B''.\\
The further a PLL is away from the reference feeding ADPLL 11 the worse performance is, peaking furthest from the reference in ADPLL 22.
The lesser cycle-to-cycle of Design ``2A'' follows from the implementation independent design of the phase detector. Unlike the inverter based design where the implementation may result in the propagation delay between taps on the delay line changing, from both tap to tap in the same detector and the same tap in different detectors, the clocked design has identical detection resolutions as each register is driven by the FPGA clock. This can be highlighted in the more easily demonstrable case of the clocked and inverter based oscillators.\\
\begin{figure}[h]%
    \centering
    \subfloat[Inverter Based Design.]{{\includegraphics[width=0.5\linewidth]{distrib_ring} }}%
    \subfloat[FPGA Clocked Design.]{{\includegraphics[width=0.5\linewidth]{distrib_pa} }}%
    \caption{Example Distribution of Periods.\label{fig:dists}}    
    \vspace{-0.5cm}
\end{figure}
Figure \ref{fig:dists} paints a picture of the unrealistic nature of the FPGA clocked design in comparison to its inverter based counterpart, each oscillator will have identical intrinsic period steps thus eliminating any jitter that maybe be seen in the system due to misalignment. This effects the suitability of the FPGA clocked designs for the improvement of simulation models, or the examination of how a novel block may impact the behaviour of the network.
\section*{Conclusion}
An FPGA is a suitable environment for the prototyping of ADPLL networks and can fill a number of roles depending on the designer's requirements. However, the designer should bear in mind the platform's limitations, especially when attempting to use a frequency that is not orders of magnitude lower than the maximum clock available from the FPGA's clock manager. Inverter based and FPGA clocked designs, both have a niche in which they are the preferred option, with the clocked design better suiting replication of an existing design at scaled-down frequencies and the inverter based designs better in the modelling and analysis of ADPLL network behaviour.

\bibliographystyle{IEEEtran}
\bibliography{conf}

### 2019-04-06 thesis/Abstract.tex
initial thesis background

\documentclass[11pt,english,british]{report}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3.5cm,rmargin=2.4cm}
\begin{document}
Low power, high frequency clock distribution systems will be in ever increasing demand in the near future as the need for high performance digital circuitry grows. At these frequencies, however, the conventional clock distribution systems are unable provide a clock signal of adequate quality without compromising on either of these problems. Many devices have turned away from using Globally Synchronous clock distribution systems in favour of those that divide the area of the chip into Globally Asynchronous but Locally Synchronous areas. However, new technologies seek to enable the use of Globally Synchronous methods at high frequencies, one of which being the use of oscillators coupled in phase, each responsible for delivering the clock to a subregion of the chip.\\
Each oscillator forms part of a Phase Lock Loop (PLL), and in order to enable the synchronisation of the network each PLL is linked those controlling the adjacent clock regions. For a digital system it is expedient to implement these PLLs digitally as an All-Digital Phase Lock Loop (ADPLL) as this provides a number of advantages. It has been shown in theory and experimentally that this method can produce the high quality clock desired with low power consumption.\\
As the production of test chips is expensive and time consuming through simulation and validation of a design is vital, traditionally carried out for mixed signal circuitry using complex behavioural and theoretical models. For a ADPLL Network the consistency of a signal both with respect to itself, and to the other clock signals on the chip is a key performance attribute and much of the variation is due to random processes that may be difficult to simulate effectively.\\
This thesis will demonstrate that the Field Programmable Gate Array (FPGA) can be used in order to simulate, model or validate ADPLL network architectures in a cost and time effective manner, as a complement to conventional methods. The key benefit is that many system dynamics that will be seen when a network is implemented on an Application Specific Integrated Circuit (ASIC), but be overlooked in software simulations can be examined in the hardware simulation that an FPGA provides.\\
This thesis implements networks using three designs of ADPLL, each using a different architecture, and highlights the use cases to which each is best suited. The performance of each design is then analysed and this compared to the suggested use cases. Additionally the impact of more minor architectural modifications is tested and documented.
\end{document}

>>>>

\documentclass[11pt,english,british]{report}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3.5cm,rmargin=2.4cm}
\begin{document}
Low power, high frequency clock distribution systems will be in ever increasing demand in the near future as the need for high performance digital circuitry grows. At these frequencies, however, the conventional clock distribution systems are unable provide a clock signal of adequate quality without compromising on either of these problems. Many devices have turned away from using Globally Synchronous clock distribution systems in favour of those that divide the area of the chip into Globally Asynchronous but Locally Synchronous areas. However, new technologies seek to enable the use of Globally Synchronous methods at high frequencies, one of which being the use of oscillators coupled in phase, each responsible for delivering the clock to a subregion of the chip.\\
Each oscillator forms part of a Phase Lock Loop (PLL), and in order to enable the synchronisation of the network each PLL is linked those controlling the adjacent clock regions. For a digital system it is expedient to implement these PLLs digitally as an All-Digital Phase Lock Loop (ADPLL) as this provides a number of advantages. It has been shown in theory and experimentally that this method can produce the high quality clock desired with low power consumption.\\
As the production of test chips is expensive and time consuming through simulation and validation of a design is vital, traditionally carried out for mixed signal circuitry using complex behavioural and theoretical models. For an ADPLL Network the consistency of a signal both with respect to itself, and to the other clock signals on the chip is a key performance attribute and much of the variation is due to random processes that may be difficult to simulate effectively.\\
This thesis will demonstrate that the Field Programmable Gate Array (FPGA) can be used in order to simulate, model or validate ADPLL network architectures in a cost and time effective manner, as a complement to conventional methods. The key benefit is that many system dynamics that will be seen when a network is implemented on an Application Specific Integrated Circuit (ASIC), but be overlooked in software simulations can be examined in the hardware simulation that an FPGA provides.\\
This thesis implements networks using three designs of ADPLL, each using a different architecture, and highlights the use cases to which each is best suited. The performance of each design is then analysed and this compared to the suggested use cases. Additionally the impact of more minor architectural modifications is tested and documented.
\end{document}
